
\chapter{CHAPTER 1}


\section{INTRODUCTION}


\subsection{OVERVIEW}
Digital art refers to forms of expression and transmission of art form with digital form. Relying on modern science and technology is the distinctive characteristics of the digital manifestation. Traditional art refers to the art form which is created before the digital art. From the recipient to analyze, it can simply be divided into visual art, audio art, audio-visual art and audio-visual imaginary art, which includes literature, painting, sculpture, architecture, music, dance, drama and other works of art. Digital art and traditional art are interrelated and interdependent. Social development is not a people's will, but the needs of human life are the main driving force anyway. The same situation happens in art. In the present circumstances, digital art and traditional art are inclusive of the symbiotic state, so we need to systematically understand the basic knowledge of the form between digital art and traditional art.\\
Traditional art developed under social conditions of the division in the body and the brain, in which the advantages of the elite art is much larger than the public art, these advantages are protected by the social hierarchy, but then they have been more advanced with the strengthen of the copyright system. The creators of traditional art are mostly artists who engaged in the research of art and design, they have a solid theoretical foundation and a keen insight of the new trend of art, and constantly adjust their own artistic ideas to adapt to new forms of art, they are creative power driven. In the digital network, anonymous login is a certain
degree of concealment. There is no hierarchy to exert its influence. It is difficulty to control the movement of art works and the copyright maintenance. The creators of digital art are an integrated group of genius, they have a certain degree of understanding of art, digital technology and other professions. They can apply the digital art to mastery, their creative energy is far more proactive than traditional artists. Of particular importance is: the digital network in the world as a major creative space for the vast majority of creators in creative concepts are no longer the same as the traditional artists, who are concerning all about to achieve the economic income through the traditional copyright, mainly reflected their values and self-realization is linked to a sense of achievement. In this sense, the advent of digital art and the non-vocational trend of the creators have expanded the digital popularity and the artistic teams.\\
Traditional art works are focus on its uniqueness and authority, the artist's original work will be regarded as a valuable asset. Underestimate the value of the copies. In the copies, the prices are usually depended on the copy quality. After the more copying times, the effect will be worse, the prices are also lower. The operation of the entire art market is guided by the above-mentioned rules. The works of digital art are clearly opposed to the works of traditional art, it is not only easy to error correction, but also measuring their value through the range of dissemination and the level of participation. In addition, there is no difference in quality
between the original and the copy, it is not necessary to cherish the original as a treasure. It will make the traditional art market inevitable in an awkward situation. Moreover, with the developments of the files' compression, restore technological progress and the concept of the formation resources sharing, an increasing number of users directly through the digital network to obtain the art works, the traditional cultural industries are impacting on a powerful attack. The MP3 music on the recent popularity of the network illustrates this point.\\
Mutually linked multimedia data as the characteristics of the hyper dia determines that it is bound to break through a smgle medium to separate the traditional pattern of art and promote the information of art become multidimensional. People can master the form of art through a variety of senses. The so-called "multimedia" is still presently referred to the integration of the audio-media information and the visual media information. In the future, the touchable-media information, the scented-media information and the testable media information can also be included. Moreover the original information of the different sensorial in the future may be able to change shape, which is one of the achievements of the hypermedia. In addition, hypermedia is breaking people' s traditional customs such as "wait and see" or "scrutinize" when they are facing art, hypermedia also is luring users to "surfing" or "roaming" on the Internet as big pleasures. Speak of the specific figure of hypermedia is manly presented as the web pages.  In the field of the digital network and the corresponding digital art network, many young people have more practical experiences than their elders, they have gained the corresponding rights to speak. Resulting in the age of the audience became younger. In the expression of digital art, human beings are often marginalized the true reality, people's emotions are virtual, so that the humanities which are frequently emphasized in traditional art have been overlooked. This neglect is not coming from the senseless of the artists,. but rather the view angle is not the same. Through virtual things, people can make impossible dreams and thoughts become possible through their participation. Network with open practice drives creators to construct a new kind of stylized art form by their own rights.

\subsection{ADVANCEMENT IN DIGITAL ART}
Digital network developed itself from the LAN to WAN, then from "three-in-one" network to "Digital Earth" which is paralleled with the historical development of the globalization trend. The management of traditional media is basically relying on the whole country, which is a vertical top-down leadership. This management in art area was embodied in a clear superior-subordinate relationship, mandatory policy or requirement. Digital network in the world is basically anarchy by now, the power of the traditional leadership for the flow of online information is beyond their capability to charge. Even if the rule of law for against the information technology and network management has been gradually strengthened in the future, it can no longer return to the situation of centralization. In such circumstances, the importance of the self-regulation between media and art will be more evident than ever, cross-cultural communication and cross-cultural conflict will also be unprecedented significant.


